### 2020-03-10 related.tex
s1-3 and letter comments
final tvcg
Updates from Overleaf

\cut{Excel allows users to maintain context during navigation
by manually creating named ranges~\cite{named-range},
that are essentially references
to a spreadsheet region,
and appear in a \emph{name box}
within the Excel menu bar.
Users can click on a named range
to navigate to the referred region.
However, the onus is on the user to create
named ranges for each region of interest.}
\stitle{Microsoft Excel.}
\new{Excel enables users to manually create references
to a spreadsheet region using the named 
ranges~\cite{named-range} feature,
accessible from the menu bar.
Users can click on a named range
to navigate to the referred region. 
However, the onus is on the user to create
named ranges for each region of interest. 
The pivot table~\cite{pivot} feature 
allows users to create a summary view to 
compare subsets of data without having to 
provides a summary view, enabling users
to compare subsets of data without
having to navigate to various locations
within the sheet.
This summary is placed
in a separate region of the spreadsheet,
preventing users from accessing
the data underlying the summary, impeding navigation. 
A similar overview feature, \code{SUBTOTAL}~\cite{subtotal},
adds a new row at the end of each distinct
subset of data with summary
information. Users can expand the summary to view
the actual spreadsheet data.
However, for datasets with many subsets (\eg for numeric data),
the number of new lines inserted (i.e., the summary) 
can itself become very
large, spanning multiple screens, and can cause
increased
visual discontinuity during navigation. Finally, NodeXL~\cite{hansen2010analyzing}
is a plug-in that provides a spreadsheet network overview
and supports navigational operations,
\eg zooming in/out, dynamic filtering, on the overview;
this plug-in only supports network datasets,
such as biological or social networks.}

\stitle{Google Sheets Explore.}
Google Sheets Explore~\cite{web:explore} provides
an overview of the data by
auto-generating charts of data statistics.
Users can specify queries to the system
(similar to a web search)
asking for different summary statistics.
While Explore
is a convenient means to understand
high-level data characteristics,
it doesn't address the
navigational challenges
related to scrolling and steering.

@@

\stitle{Tabular Data Analysis (TDA).}
Visualization tools such as Tableau~\cite{tableau}, Power BI~\cite{powerbi}, Keshif~\cite{yalccin2018keshif}, Voyager~\cite{wongsuphasawat2016voyager} and
analytical tools such as SPSS~\cite{noruvsis1986spss}, SAS~\cite{sas1985sas}, can all provide summaries of tabular data in various forms (visualizations,
aggregate statistics). 
\new{These summaries 
are static overviews of the data---much like pivot tables, 
these summaries are not dynamically linked
to nor are co-located with
the underlying raw data. 
For example, Keshif~\cite{yalccin2018keshif} can display all the unique values corresponding to an attribute of interest, \eg cities of the Airbnb data~\cite{web:airbnb}. However, users cannot view or inspect the raw data corresponding to each city
in a spreadsheet-like tabular setting, while being able to
edit this raw data at will. 
With TDA tools, the spreadsheet look-and-feel is lost,
and as a result, users
lose the ability to directly manipulate raw data, derive new data, and issue formulae for free-form analysis.  
\cut{For example, using these tools users cannot \code{browse} subsets of data and \code{lookup} or \code{locate} data points of interest (see Table~\ref{tab:scope}). Aditya: previous line problematic: they can... because all these tools support to varying extents the typology. Even users of such tools want to inspect the underlying data to verify the summary statistics and visualizations~\cite{2017trust}. Aditya:this line is problematic too... because the citation is to an AQP tool rather than some general purpose study}
Therefore, the goals of spreadsheets differ from TDA 
tools in two ways: a) facilitating direct manipulation of raw 
data in-situ and b) enabling arbitrary derivation of new data and summaries
using various operations involving navigation,
\eg formulae or expressions\agp{expressions?}.
\noah being a plug-in to spreadsheets, 
provides a unified interface that
upholds both these goals
while enhancing
navigational capabilities
for spreadsheet users.
}

>>>>

\cut{Excel allows users to maintain context during navigation
by manually creating named ranges~\cite{named-range},
that are essentially references
to a spreadsheet region,
and appear in a \emph{name box}
within the Excel menu bar.
Users can click on a named range
to navigate to the referred region.
However, the onus is on the user to create
named ranges for each region of interest.}
\stitle{Microsoft Excel.}
\new{Excel enables users to manually create references
to a spreadsheet region using the named 
ranges~\cite{named-range} feature,
accessible from the menu bar.
Users can click on a named range
to navigate to the referred region. 
However, the onus is on the user to create
named ranges for each region of interest. 
The pivot table~\cite{pivot} feature 
allows users to create a summary view to 
compare subsets of data without having to 
navigate to various locations
within the sheet.
This summary is placed
in a separate region of the spreadsheet,
preventing users from accessing
the data underlying the summary, impeding navigation. 
A similar overview feature, \code{SUBTOTAL}~\cite{subtotal},
adds a new row at the end of each distinct
subset of data with summary
information. Users can expand the summary to view
the actual spreadsheet data.
However, for datasets with many subsets (\eg for numeric data),
the number of new lines inserted (i.e., the summary) 
can itself become very
large, spanning multiple screens, and can cause
increased
visual discontinuity during navigation. Finally, NodeXL~\cite{hansen2010analyzing}
is a plug-in that provides a spreadsheet network overview
and supports navigational operations,
\eg zooming in/out, dynamic filtering, on the overview;
this plug-in only supports network datasets,
such as biological or social networks.}

\stitle{Google Sheets Explore.}
Google Sheets Explore~\cite{web:explore} provides
an overview of the data by
auto-generating charts of data statistics.
Users can specify queries to the tool
(similar to a web search)
asking for different summary statistics.
While Explore
is a convenient means to understand
high-level data characteristics,
it doesn't address the
navigational challenges
related to scrolling and steering.

@@

\stitle{Tabular Data Analysis (TDA).}
Visualization tools such as Tableau~\cite{tableau}, Power BI~\cite{powerbi}, Keshif~\cite{yalccin2018keshif}, Voyager~\cite{wongsuphasawat2016voyager} and
analytical tools such as SPSS~\cite{noruvsis1986spss}, SAS~\cite{sas1985sas}, can all provide summaries of tabular data in various forms (visualizations,
aggregate statistics). 
\new{These summaries 
are static overviews of the data---much like pivot tables, 
these summaries are not dynamically linked
to nor are co-located with
the underlying raw data. 
For example, Keshif~\cite{yalccin2018keshif} can display all the unique values corresponding to an attribute of interest, \eg cities of the Airbnb data~\cite{web:airbnb}. However, users cannot view or inspect the raw data corresponding to each city
in a spreadsheet-like tabular setting, while being able to
edit this raw data at will. 
With TDA tools, the spreadsheet look-and-feel is lost,
and as a result, users
lose the ability to directly manipulate raw data, derive new data, and issue formulae for free-form analysis.  
Therefore, the goals of spreadsheets differ from TDA 
tools in two ways: a) facilitating direct manipulation of raw 
data in-situ and b) enabling arbitrary derivation of new data and summaries
using various operations involving navigation,
\eg issuing formulae.
\noah being a plug-in to spreadsheets, 
provides a unified interface that
upholds both these goals
while enhancing
navigational capabilities
for spreadsheet users.
}
